Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-09 awipev-CO2.Rmd

@@

### **Corrected Contros vs calculated *p*CO~2~ data**
```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)

@@

### **seaFET calibration constante E0**

>>>>

```{r TA 2nd cleaning , echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}

@@

### **Corrected Contros vs calculated *p*CO~2~ data**

```{r pCO2 2nd cleaning, echo=FALSE, warning=FALSE, message=FALSE}

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)

@@

### **seaFET data cleaning**

```{r seaFET 2nd cleaning, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}

```                
### **seaFET calibration constante E0**
